\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}


%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{1pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{5pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Viktor Filinkov} & \textbf{\today} \\
Senior Software Developer / Software Security Engineer & \href{mailto:dev@itsai.org}{dev@itsai.org} \\
\href{https://github.com/RussianBruteForce}{GitHub} & \href{https://www.linkedin.com/in/ViktorFilinkov}{LinkedIn}\\
\end{tabular*}
\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Meticulous and detail-oriented Software Developer with dedication to quality. I know a variety of tools and that made me talented for developing innovative solutions to unusual and difficult problems. In spare time I do cybersecurity, radio and contributions to public projects. Linux user from 2008 and the member of \href{http://omsklug.com}{OmskLUG}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Highlights}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
	\item C++ expert
	\item Low-level programming
	\item GUI/Mobile/Web/TUI
	\item Libraries
	\item Not language-tied
	\item Deploy experienced
	\item Fast learner
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	I studied programming from 14 years by myself. It was C, then C++, Python, D, Lua. After school graduation I already have had many nice projects like \href{https://www.linux-apps.com/p/1132288/}{Hachmei}, \href{https://www.linux-apps.com/p/1131188}{Qtnp}, etc. My school was a customer for most of them. While studying at university I lift up my level to immense. University's tasks were simple; I published most of sources written for my friends and teachers (\href{https://github.com/RussianBruteForce/univer}{link}). For self-proofing of language independence I implement labs for Computational Math in C, D, Lua, Python and C++ (\href{https://github.com/RussianBruteForce/Computational-Math}{link}) and matrix solver in D (\href{https://russianbruteforce.github.io/rarr/}{link}).
	
	My quick list technology stack: Linux, Git, CMake, UML, Python, C, C++, Docker, STL+GSL, Qt4 (legacy code support), Qt5, MongoDB, PostgresSQL, Android (C/C++/Java/JNI), Web Backend(Node.js/Twisted/Bottle/Proxygen/WebSocket++/libevent). Also I prefer TDD in many cases of developing process (via Google Test).
	
	With OmskLUG I participated in \href{http://omsklug.com/members/chemtech/activity/759}{Yandex.Root} and \href{https://vk.com/geohackathon}{Geohackathon} ("Green Light" project).
	
	At Crystalnix I got experience in both low and high-level programming. Boost, MongoDB, POSIX.1.b async IO (network), console tools, GUI frontends, cross-platform, legacy code support, tool adaption, Linux packages, Windows installers, OS X bundles, build pipelines, Docker images --- that's not the whole story of my practice. My favorite tools: ag, emacs, gdb, radare2, cpplint, cppcheck, clang-format.
	
	The last project I worked on was \href{http://serverauditor.com/}{Serverauditor} --- a desktop and mobile SSH terminal.
	
	After relocation to Saint Petersburg I was hired by Systems Of Artificial Intelligence (\href{https://itsai.org}{itsai.org}) as Lead/Senior Software Developer and Software Security Engineer.
	Here I worked on a lot of great projects, let's look at them:
	\begin{itemize}
		\item \href{https://smma.pro/}{\emph{SMMA}} --- Shoot Me My Account is an authentication system prototype written in C++; a bunch of technologies was involved, like WebSockets\&HTTP, JSON, video processing and object (face) recognition. Written and maintained by me. Read more on \href{https://smma.pro/}{site} and \href{https://github.com/saicorp/SMMA/wiki}{wiki} pages. \href{https://youtu.be/X2SRc-d5yBA}{Video}(rus)
		\item \href{https://itsai.org/products/view/sai-sender}{\emph{SAI Sender}} --- software for email delivery, also written in C++ with Qt5 UI. First versions (up to 1.5) based on Widgets, now it uses QML to draw UI. It supports IP blocking bypass using Tor or SOCKS, allows you to have many modifications of your messages/headers, automatic name (anything, actually) insertion and attachments. With simple usage and good flexibility SAI Sender is the best tool of its kind. We maintain versions for Windows and Linux. Also there is a server written in Python to protect Sender from unlawful distribution.
		\item \href{https://angelsos.ru/}{\emph{AngelSOS}} --- Android app (Java) and server (Node.js). Geo positioning, WebRTC, WebSockets, REST, Google Maps API, Express, handlebars, sessions, many-to-many relations, passport.js, Retrofit2, ORMLite, etc. My first site and first experience in ES6 both on web front\&back.
		\item \emph{SAI Recorder} --- not yet published secure Android call recorder. Java/JNI/C++/Qt5/QML/SQLCipher.
	\end{itemize}
	
	
	Have some experience in DDOS protection. Systems of Artificial Intelligence is a Gold partner of \href{https://stormwall.pro/en/}{StromWall} --- cloud protection against DDoS-attacks.
	
	There was some projects for escape rooms:
	\begin{itemize}
		\item Dragon game for \href{http://neoskazka.ru/index.html}{Parareal} (quests in reality). Multi-player 3D game for their escape room based on Unity3D (yeah, C\#). Linux\&Windows\&macOS versions. That was interesting experience.
		\item Software for \href{http://starwarsroom.ru/}{Star Wars Quest}. 2 Android (mostly C++) apps: for phones and tablet, 5 apps for Linux, one for Windows (C++/Qt5/QML/multi-monitor support) and server-side app to control games and room hardware (Arduino-based). I developed nice-and-simple semi-auto deployment system for this project.
	\end{itemize}
	
	In my \href{https://github.com/RussianBruteForce}{GitHub} profile you could find some interesting things on ¨Public Activity¨ and ¨Repositories¨ tabs. Some repos are fun-guarantee.

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Reviews}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

It was cool to work with Viktor. He is a very smart guy, he knows a lot about C++ and doesn't stop learning. Once he will start using spaces for indentation he will be the best C++ programmer in the world after me.

\begin{flushright}
	
\textbf{Vadim Zakondyrin}

Senior Software Developer at Crystalnix
\end{flushright}


Victor is an intelligent guy. He has own view of the world and he is keen on IT technologies especially C++. In spite of his great knowledge, Victor is at the beginning of his professional way and he should still learn to work in team and find compromises between ideal things and the real life. However, I'm sure that he will be able to manage with this task with time.

\begin{flushright}
	
	\textbf{Kirill Yakovenko}
	
	Project Manager at Crystalnix
\end{flushright}


You may ask for more recommendations here:

\href{mailto:omsk@crystalnix.com}{omsk@crystalnix.com}

+7 (3812) 500-851 

\textbf{Artur Vetershpan}, General manager at Crystalnix Omsk

\end{document}
